Low Dimensional Embedding of Climate Data for Radio Astronomical Site Testing in the Colombian Andes

### 2017-09-15 pasp/paperclimate.tex
before lores

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{opac.pdf}
\caption{Atmospheric opacity models for the Colombian Andes for different precipitable water vapor (pwv) values corresponding to three scenarios: \textit{Red line} (20 mm pwv) a 2600 masl site with 90\% relative humidity at 13$^\circ$C, \textit{Blue line} (10 mm pwv) a 3400 masl site with 90\% relative humidity at 0$^\circ$C, \textit{Red line} (2 mm pwv) a 3400 masl site with 30\% relative humidity at 0$^\circ$C.}\label{opac}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{opac.pdf}
\caption{Atmospheric opacity models for the Colombian Andes for different precipitable water vapor (pwv) values corresponding to three scenarios: \textit{Red line} (20 mm pwv) a 2600 masl site with 90\% relative humidity at 13$^\circ$C, \textit{Blue line} (10 mm pwv) a 3400 masl site with 90\% relative humidity at 0$^\circ$C, \textit{Green line} (2 mm pwv) a 3400 masl site with 30\% relative humidity at 0$^\circ$C.}\label{opac}
\end{center}
\end{figure}
